---
title: "Stem Completion"
author: "Arpita Shah and Tian Zheng"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = "..")
```

HappyDB is a corpus of 100,000 crowd-sourced happy moments via Amazon's Mechanical Turk. You can read more about it on https://arxiv.org/abs/1801.07746

In this R notebook, we process the raw textual data for our data analysis.

### Step 0 - Load all the required libraries

From the packages' descriptions:

+ `tm` is a framework for text mining applications within R;
+ `tidyverse` is an opinionated collection of R packages designed for data science. All packages share an underlying design philosophy, grammar, and data structures;
+ `tidytext` allows text mining using 'dplyr', 'ggplot2', and other tidy tools;
+ `DT` provides an R interface to the JavaScript library DataTables.

```{r load libraries, warning=FALSE, message=FALSE}
library(tm)
library(tidytext)
library(tidyverse)
library(DT)
```

### Step 1 - Load the data to be cleaned and processed

```{r read data, warning=FALSE, message=FALSE}
urlfile <- "https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/cleaned_hm.csv" # nolint
hm_data <- read_csv(urlfile)
```

### Step 2 - Preliminary cleaning of text

We clean the text by converting all the letters to the lower case, and removing punctuation, numbers, empty words and extra white space and removing the stopwords and words that aren't relevant for our analysis.

```{r text processing in tm}
corpus <- VCorpus(VectorSource(hm_data$cleaned_hm)) % > %
  tm_map(content_transformer(tolower)) % > %
  tm_map(removePunctuation) % > %
  tm_map(removeNumbers) % > %
  tm_map(removeWords, stopwords("english")) % > %
  tm_map(removeWords, c(
    "happy", "got", "made", "went", "ago", # nolint
    "yesterday", "lot", "today", "months", "month", # nolint
    "happier", "happiest", "last", "week", "past"
  )) % > %
  tm_map(stripWhitespace)

```

### Step 3 - Converting tm object to tidy object

Convert the "tm" object to a "tidy" object for much faster processing and so that it can be combined back with the original dataframe.

```{r stemming}
cleaned_text <- tidy(corpus)  %>%
  select(text)
```

### Step 4 - Combine the cleaned texts with the original dataframe

```{r tidy dictionary}
hm_data <- cbind(hm_data, CleanedText = cleaned_text)
```

### Exporting the processed text data into a CSV file

```{r export data}
write_csv(hm_data, "./output/processed_moments.csv") # nolint
```

The final processed data is ready to be used for any kind of analysis.